### 2013-05-17 menger.tex
added simple result to sorgenfrey
Proved irrational sorgenfrey result for any dense subset

  Due to Telgarski in ``On Games of Topsoe'':

  \begin{theorem}
    For metrizable $X$, $X$ is $\sigma$-compact if and only if $F \win \mengame{X}$.
  \end{theorem}

@@

  \begin{theorem}
    For regular spaces $X$, $F \markwin \mengame{X}$ if and only if $X$ is $\sigma$-compact.
  \end{theorem}

@@

  \begin{example}
  Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed. This space is non-regular, non-$\sigma$-compact, and Lindel\"of.
  \end{example}

  \begin{proof}
  From Counterexamples: The rationals are closed, but the closure of any open neighborhood is the whole real line, so they cannot be separated from any irrational point. Compact sets in this topology are nowhere dense in the Euclidean topology, so there cannot be countably many which union to the whole space. $\{(a,b)\setminus D : a,b\in\mathbb{Q},D\in\{\emptyset,\mathbb{Q}\}\}$ is a countable base for the space, and second-countability implies Lindel\"of.
  \end{proof}

>>>>

  Due to Telgarski in ``On Games of Topsoe'' (along with $\sigma$-compact implying $F\markwin \mengame{X}$).

  \begin{theorem}
    For metrizable $X$, $X$ is $\sigma$-compact if and only if $F \win \mengame{X}$ if and only if $F\markwin \mengame{X}$.
  \end{theorem}

@@

  \begin{theorem}
    For regular spaces $X$, $X$ is $\sigma$-compact if and only if $F \markwin \mengame{X}$.
  \end{theorem}

@@

  \begin{example}
  Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed. This space is non-regular, non-$\sigma$-compact, and Lindel\"of.

  This space is an example of non-$\sigma$-compact but $F \markwin \mengame{R}$ (and is thus also Menger).
  \end{example}

  \begin{proof}
  From Counterexamples: The rationals are closed, but the closure of any open neighborhood is the whole real line, so they cannot be separated from any irrational point. Compact sets in this topology are nowhere dense in the Euclidean topology, so there cannot be countably many which union to the whole space. $\{(a,b)\setminus D : a,b\in\mathbb{Q},D\in\{\emptyset,\mathbb{Q}\}\}$ is a countable base for the space, and second-countability implies Lindel\"of.

  % To see Menger, let $\mc{U}_0,\mc{U}_1,\dots$ be a sequence of open covers, and choose open sets $U_{2n}\in\mc{U}_{2n}$ which cover $q_n$ for each $q_n\in\mathbb{Q}$ (which in turn are open in the Euclidean line). Since the complement of the union $\bigcup_{n<\omega} U_{2n}$ must be closed discrete in the Euclidean line, it is countable, so open sets $U_{2n+1}\in\mc{U}_{2n+1}$ may be found to cover the remainder.

  To see $F \markwin \mengame{R}$, we define $\sigma(\mc{U}_{2n},2n)$ to be a finite cover of $[-n,n]\setminus\mathbb{Q}$, and $\sigma(\mc{U}_{2n+1},2n+1)$ to be a finite cover of $\{q_n\}$ for each $q_n\in\mathbb{Q}$.
  \end{proof}

### 2013-05-17 sorgenfrey/sorgenfrey.tex
Proved irrational sorgenfrey result for any dense subset

\begin{proposition}
Let $R$ be the Sorgenfrey line, the set of real numbers with the topology generated by the base $\mc{B} = \{[a,b): a<b\in R\}$ (where $[a,b) = \{x : a\leq x < b\}$).

@@

>>>>

\begin{proposition}
Let $R$ be the Sorgenfrey line, the set of real numbers with the topology generated by the base $\mc{B} = \{[a,b): a<b\}$ (where $[a,b) = \{x : a\leq x < b\}$).

@@

This idea can be generalized for the irrationals, but it takes some machinery:

\begin{theorem}
Let $P$ be a dense subspace of the Sorgenfrey line with the induced topology, which has the base $\mc{B} = \{[a,b) : a<b, a\in P\}$.

For every $\mc{C}\subseteq\mc{B}$ which is also a base for $P$, there exists a pairwise disjoint subcover $\mc{C}'\subseteq\mc{C}$ (and thus a locally finite subcover).
\end{theorem}
\newpage
\begin{proof}
It suffices to show for $[0,1)\cap P$. We begin by constructing a collection of functions $S\subseteq \omega^{\omega_1}$ and numbers $c_s$, $d_s$ defined by those functions as follows:
  \begin{itemize}
    \item Let $S_0 = \{\emptyset\}$. Let $d_{\emptyset}=0$ and $c_{\<-1\>}=1$.
    \item Suppose $S_\alpha$ has been defined, as well as $d_s\leq c_{s\concat\<-1\>}$. For $s\in S$, consider the following:
      \begin{itemize}
        \item If $d_s = c_{s\concat\<-1\>}$, do nothing.
        \item If $d_s < c_{s\concat\<-1\>}$ and $d_s\in P$, let $S_{\alpha+1}$ contain $s\concat\<0\>$ and define $c_{s\concat\<0\>}$, $d_{s\concat\<0\>}$, $c_{s\concat\<0,-1\>}$ such that 
          \[
            d_s = c_{s\concat\<0\>} < d_{s\concat\<0\>} \leq c_{s\concat\<0,-1\>} = c_{s\concat\<-1\>}
          \]
        where $[c_{s\concat\<0\>}, d_{s\concat\<0\>})\in \mc{C}$.
        \item If $d_s < c_{s\concat\<-1\>}$ and $d_s\in P$, let $S_{\alpha+1}$ contain $s\concat\<n\>$ for all $n<\omega$ and define $c_{s\concat\<n\>}$, $d_{s\concat\<n\>}$, $c_{s\concat\<n,-1\>}$ for all $n<\omega$ such that
          \[
            d_s < \dots \leq c_{s\concat\<2,-1\>} = c_{s\concat\<1\>} < d_{s\concat\<1\>} \leq c_{s\concat\<1,-1\>} = c_{s\concat\<0\>} < d_{s\concat\<0\>} \leq c_{s\concat\<0,-1\>} = c_{s\concat\<-1\>}
          \]
        where $[c_{s\concat\<n\>}, d_{s\concat\<n\>})\in \mc{C}$ for all $n<\omega$ and $c_{s\concat\<n\>} \rightarrow d_s$.
      \end{itemize}
    \item Suppose $\alpha$ is a limit ordinal and $S_\beta$ has been defined for all $\beta<\alpha$. If $s\in\omega^\alpha$ and $t\in \bigcup_{\beta<\alpha}S_\beta$ for all $t<s$, let $S_\alpha$ contain $s$ and define $d_s = \lim_{t<s}d_t$ and $c_{s\concat\<-1\>} = \lim_{t<s} c_{t\concat\<-1\>}$.
  \end{itemize}

  By construction, $\mc{C}' = \{[c_s,d_s) : s\in S\}$ is a disjoint subcollection of $\mc{C}$. We claim it also must cover $[0,1)\cap P$.

  Suppose not: $x\in[0,1)\cap P$ is not contained in $[c_s,d_s)$ for any $s\in S$. Note that $d_\emptyset<x$ (or else $x\in[c_{\<0\>},d_{\<1\>}$)). Assume $n_\beta<\omega$ is defined for all $\beta<\alpha$, and consider $s\in\omega^\alpha$ where $s(\beta)=n_\beta$. If $d_s<x$, we claim there is a minimal $n_\alpha<\omega$ where $d_{s\concat\<n_\alpha\>}<x$.
    \begin{itemize}
      \item This possible when $d_s\not\in P$ since $d_{s\concat\<n\>}\to d_s$.
      \item This is also possible when $d_s\in P$ since $[c_{s\concat\<0\>},d_{s\concat\<0\>})$ does not contain $x$, and thus $d_s=c_{s\concat\<0\>}<d_{s\concat\<0\>}\leq x$. If $d_{s\concat\<0\>} = x$ then $d_{s\concat\<0\>}\in P$ and $[d_{s\concat\<0\>},d_{s\concat\<0,0\>})=[c_{s\concat\<0,0\>},d_{s\concat\<0,0\>})$ contains $x$, which is a contradiction.
    \end{itemize}

  Finally, we notice that by defining $f\in\omega^\omega_1$ such that $f(\alpha)=n_\alpha$, then $d_{f(\alpha)}$ is an increasing sequence defined for all $\alpha<\omega_1$, which is a contradiction.
\end{proof}
